BSOS

### 2014-06-08 Paper.tex
added some things

\paragraph{Interrupts}
Interrupts are also very important. Interrupts create an efficient way for the OS to interact with its environment. Older systems used to monitor different sources of input for events. Interrupts help automatically save local register contexts and run particular code in response to particular events. Interrupts cause the current program to pause for a moment, save it, and then run code associated with that interrupt. In other words, an interrupt interrupts the program-hence the name. Interupts are handles by the kernel.

@@

\paragraph{}
On ARM-based machines, specifically those with Cortex-M3 processors, the bootstrapping process is remarkably similar. Despite the RISC (Reduced Instruction Set Computing) nature of the ARM architecture

@@

Information is se4nt from the keyboard to the processor via a standard protocol. Inside any commercial keyboard is a tiny computer chip

>>>>

\paragraph{Interrupts}
Interrupts are also very important. Interrupts create an efficient way for the OS to interact with its environment. Older systems used to monitor different sources of input for events. Interrupts help automatically save local register contexts and run particular code in response to particular events. Interrupts cause the current program to pause for a moment, save it, and then run code associated with that interrupt. In other words, an interrupt interrupts the program-hence the name. Interrupts are handled by the kernel.

@@

\paragraph{}
On ARM-based machines, specifically those with Cortex-M3 processors, the bootstrapping process is remarkably similar. Despite the RISC nature of the Cortex-M3, a similar chain of events takes place: the stack is set, the kernel is loaded from disk, and the system performs a far jump to the first instruction of the kernel, allowing it to take control.

@@

Information is sent from the keyboard to the processor via a standard protocol. Inside any commercial keyboard is a tiny computer chip
